---
title: "Data Quality Evaluation with inspectEHR"
author: "Edward Palmer"
date: "20th September 2019. Updated: `r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Data Quality Evaluation with inspectEHR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The primary role of `inspectEHR` is to process the data inside CC-HIC in such a way as to make it ready to produce a data quality report.

First, install and load `inspectEHR` from github, or download the latest release directly.

```{r, eval = FALSE}
# If you need inspectEHR
remotes::install_github("DocEd/inspectEHR")
library(inspectEHR)

## Establish a database connection using DBI
## Details omitted here for security
ctn <- DBI::dbConnect()
output_path <- "where/i/want/to/save"
```

Supply the `perform_evaluation` function with an output folder.
Please note, you must have write access to both the database and output folder for this to work.
You can optionally supply a table with lookups for each contributing site, to conceal the site level identity
of any output.
The verbose argument is useful to keep track of progress and to debug if there are any issues.

```{r, eval = FALSE}
perform_evaluation(connection = ctn,
                   output_folder = output_path,
                   verbose = TRUE)
```

