---
title: "Data extraction using inspectEHR"
author: "Edward Palmer"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Data extraction using inspectEHR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`inspectEHR` contains a number of helper functions for direct data extraction.
The focus of data extraction in `inspectEHR` is to facilitate data quality evaluation.
As a result, the data extraction is optimised for extracting a single data item or closely related data items.
This approach is unlikely to be of direct use to analyst, who will likely need
to extract a large number of different concepts for a specific patient cohort.
In this latter case use, please refer to the `wranglEHR` package, which is optimised for this purpose.

In order to use `inspectEHR` you first need to install it with:

```{r, eval = FALSE}
# If you need inspectEHR
remotes::install_github("DocEd/inspectEHR")
```

Now load `inspectEHR`, establish a database connection and make the `core` table.
The `core` table is a remote query that includes all correct joins, so that you know it is safe to work with.

```r
library(inspectEHR)

## Establish a database connection using DBI
## Details omitted here for security
ctn <- DBI::dbConnect()
core <- make_core(ctn)
```

```{r, include = FALSE}
library(inspectEHR)
core <- make_core(.debug = TRUE)
```

Now you can extract whatever data you wish with the `extract` function.
This is the `S3` generic that will apply the correct method to extract a specified CC-HIC event.

```{r}
# Extract Heart Rates
hr <- extract(core, code_name = "NIHR_HIC_ICU_0108")
knitr::kable(head(hr, 10))
```

The event has been extracted into a standardised format, including other features that are typically useful when evaluating the context of data quality (e.g. where and when the data originated).

More complex data item extraction is also possible, and requires no further effort than seen above.
We can demonstrate with central venous pressure (CVP), which contains metadata.

```{r}
# Extract CVP
cvp <- extract(core, code_name = "NIHR_HIC_ICU_0116")
knitr::kable(head(cvp, 10))
```

Now you can see an additional column containing the correct metadata.
All column classes are handled automatically, including all metadata and timestamps for more complex data items.
In this way the end user can be sure that the whole event has been extracted, without referring to the CC-HIC data model (which is not intuitive to interpret).

The extracted event is tagged with some useful attributes: `code_name` and `class`.

```{r}
attr(hr, "code_name")
class(hr)
```

The class encodes the temporally of the event (is it time variant or not) and the data type (integer, string, real etc.).
This is useful in method dispatch when writing data quality evaluation functions.
The methods currently available for a class can be viewed with `methods()`

```{r}
methods(class = "integer_1d")
```
